### 2020-03-25 Common/chapters/deep_learning.tex
Julien and Johan: typos

\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}Machine learning algorithms can be belong to two classes. The first one is "supervised learning". It includes learning algorithms whose training samples are associated with their labels in order to find the optimal mapping between the input and the output. The second one is "unsupervised learning". In contrast to supervised algorithms, the latter rely on unlabeled data. Its main goal is to infer the natural structure  present in the data. As the models presented in this work belong to the "supervised learning" category, notions explained below refer to this kind of algorithms.

@@

\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}In deep learning, data is essential. As seen previously, neural networks learn features from it. Therefore, data has to be handled carefully and in the right way. Usually, it is split into three different sets:
\begin{itemize}
\item The training set: This is the part of the dataset that is used to train the neural network (the weights and biases).
\item The validation set: This dataset is used to evaluate a trained model. Usually, the evaluation on the validation set is performed every $N$ epochs, where $N$ is a fixed number. The validation set needs to come from the same distribution as the training set but should exclusively contain unseen data. This last point is crucial since the validation set shows how well the neural network generalizes on unknown data. The validation set can also be used as an indicator to decide when the training should be stopped in order to prevent "overfitting" which is the behaviour of a model that fits to the training set too closely and do not generalize well. In fact, if the validation loss continuously increases for a certain number of epochs, going on with the training will increase the overfit. The fact of interrupting the training earlier is called "early stopping".
\item The test set: This last part of the dataset is used to establish the final evaluation of the model. It also contains unseen data exclusively. 
\end{itemize}
The way these three sets are split mostly depends on the number of samples available. If the latter is big, the data is split into training and test sets using the ratio 80/20. Then, the remaining training samples are also split into training and validation using the ratio 80/20. On the contrary, if there are few data available, k-fold cross-validation is a good practice. This technique consists in splitting the entire dataset into k folds. One fold is picked as test set and the others are considered as training sets. The model is trained on training folds and tested on the test fold. Then, another test set is picked and the same process is repeated until all possible tests set are picked. At the end of the process, the results of all test sets are averaged, which provides a good estimation of the model's performance. This technique is summarized on Figure \ref{cross_validation}.

>>>>

\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}Machine learning algorithms can belong to two classes. The first one is "supervised learning". It includes learning algorithms whose training samples are associated with their labels in order to find the optimal mapping between the input and the output. The second one is "unsupervised learning". In contrast to supervised algorithms, the latter rely on unlabeled data. Its main goal is to infer the natural structure  present in the data. As the models presented in this work belong to the "supervised learning" category, notions explained below refer to this kind of algorithms.

@@

\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}In deep learning, data is essential. As seen previously, neural networks learn features from it. Therefore, data has to be handled carefully and in the right way. Usually, it is split into three different sets:
\begin{itemize}
\item The training set: This is the part of the dataset that is used to train the neural network (the weights and biases).
\item The validation set: This dataset is used to evaluate a trained model. Usually, the evaluation on the validation set is performed every $N$ epochs, where $N$ is a fixed number. The validation set needs to come from the same distribution as the training set but should exclusively contain unseen data. This last point is crucial since the validation set shows how well the neural network generalizes on unknown data. The validation set can also be used as an indicator to decide when the training should be stopped in order to prevent "overfitting" which is the behaviour of a model that fits to the training set too closely and do not generalize well. In fact, if the validation loss continuously increases for a certain number of epochs, going on with the training will increase the overfit. The fact of interrupting the training earlier is called "early stopping".
\item The test set: This last part of the dataset is used to establish the final evaluation of the model. It also contains unseen data exclusively. 
\end{itemize}
The way these three sets are split mostly depends on the number of samples available. If the latter is big, the data is split into training and test sets using the ratio 80/20. Then, the remaining training samples are also split into training and validation using the ratio 80/20. On the contrary, if there are few data available, k-fold cross-validation is a good practice. This technique consists in splitting the entire dataset into k folds. One fold is picked as test set and the others are considered as training sets. The model is trained on training folds and tested on the test fold. Then, another test set is picked and the same process is repeated until all possible test sets are picked. At the end of the process, the results of all test sets are averaged, which provides a good estimation of the model's performance. This technique is summarized on Figure \ref{cross_validation}.

### 2020-03-25 Common/chapters/introduction.tex
Julien and Johan: typos

First of all, used as an extra diagnosis, they can decrease the probability of missing positive diagnoses. Then, they can also speed up the diagnosis process by proposing regions of interest to clinicians, which, in time, could reduce the screening costs. Similarly, lower screening costs imply a greater accessibility to screening tests, which can result in an earlier cancer detection. As stated before, detecting cancers at an early stage maximizes the probability of curing them. Another benefit of using CAD systems (especially the ones based on deep learning) is the number of cases that the latter are trained on. In fact, in order to built efficient deep learning models, large amounts of data are required. Consequently, efficient CAD systems usually see a lot more cancer cases than beginner clinicians.

@@

\section{Contributions}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}%This work proposes a state-of-the-art deep learning model for prostate lesion classification and proposes a method based on transfer learning using different body parts to overcome the lack of publicly available data in the medical field. Concretely, the major contributions of this work are:
The major contributions of this work are:
\begin{itemize}
\item A state-of-the-art deep learning model for prostate cancer classification. To make the experiment completely reproductible, all steps are clearly described, the corresponding scripts are available on GitHub\footnote{\url{https://github.com/eXascaleInfolab/2019_Hospital-Fribourg}} and the raw results are presented.

>>>>

First of all, used as an extra diagnosis, they can decrease the probability of missing positive diagnoses. Then, they can also speed up the diagnosis process by proposing regions of interest to clinicians, which, in time, could reduce the screening costs. Similarly, lower screening costs imply a greater accessibility to screening tests, which can result in an earlier cancer detection. As stated before, detecting cancers at an early stage maximizes the probability of curing them. Another benefit of using CAD systems (especially the ones based on deep learning) is the number of cases that the latter are trained on. In fact, in order to build efficient deep learning models, large amounts of data are required. Consequently, efficient CAD systems usually see a lot more cancer cases than beginner clinicians.

@@

\section{Contributions}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}%This work proposes a state-of-the-art deep learning model for prostate lesion classification and proposes a method based on transfer learning using different body parts to overcome the lack of publicly available data in the medical field. Concretely, the major contributions of this work are:
The major contributions of this work are:
\begin{itemize}
\item A state-of-the-art deep learning model for prostate cancer classification. To make the experiment completely reproducible, all steps are clearly described, the corresponding scripts are available on GitHub\footnote{\url{https://github.com/eXascaleInfolab/2019_Hospital-Fribourg}} and the raw results are presented.

### 2020-03-25 Common/chapters/paper_reproduction.tex
Julien and Johan: typos

\subsubsection{Methodology}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}The methodology described in this section is the closest replication possible of the authors' data processing methodology. Most of it were reproductible in a similar way, apart from the manual lesion contouring which was performed by a qualified radiologist in the authors' case. Furthermore, the authors did not mention any participation in the official PROSTATEx challenge.

@@

An important part of this process is the normalization. In fact, images were normalized before beeing stacked, based on a Z-score, i.e. 
\begin{equation}
\label{eq:normalization}
	Pixel_{{i,j}_{normalized}} = \frac{Pixel_{i,j} - \mu}{\sigma}
\end{equation}
\noindent where $Pixel_{i,j} \in [0,255]$ is a grayscale pixel value, $\mu$ is the mean value of all images of the corresponding sequence for this patient and $\sigma$ the standard deviation of all images of the corresponding sequence for this patient. According to the authors, normalizing each sequence of each patient separately allows to keep slight contrast nuances which ultimately help the final diagnosis. In other words, all T2-weighted images belonging to a specific patient were concatenated into a single NumPy array. Then, the mean and standard deviation of the array were computed. These values served as $\mu$ and $\sigma$ to normalize the T2-images of this specific patient. The equivalent was applied to the patient's DWI and ADC images, and the same process was employed for all patients separately.
Then, the dataset was augmented in the same way as the authors. Concretely, images were rotated ($-20$ to $20^\circ$), flipped horizontally (probability of $0.5$) and shifted horizontally (value $\in [-1, 0, 1]$ pixel). These techniques alone allowed to create a large enough amount of data. Therefore, two other augmentation methods used by the authors (horizontal stretching by a \mbox{factor $\in [0.9,1.1]$} and vertical shifting) were not used.

>>>>

\subsubsection{Methodology}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}The methodology described in this section is the closest replication possible of the authors' data processing methodology. Most of it were reproducible in a similar way, apart from the manual lesion contouring which was performed by a qualified radiologist in the authors' case. Furthermore, the authors did not mention any participation in the official PROSTATEx challenge.

@@

An important part of this process is the normalization. In fact, images were normalized before being stacked, based on a Z-score, i.e. 
\begin{equation}
\label{eq:normalization}
	Pixel_{{i,j}_{normalized}} = \frac{Pixel_{i,j} - \mu}{\sigma}
\end{equation}
\noindent where $Pixel_{i,j} \in [0,255]$ is a grayscale pixel value, $\mu$ is the mean value of all images of the corresponding sequence for this patient and $\sigma$ the standard deviation of all images of the corresponding sequence for this patient. According to the authors, normalizing each sequence of each patient separately allows to keep slight contrast nuances which ultimately help the final diagnosis. In other words, all T2-weighted images belonging to a specific patient were concatenated into a single NumPy array. Then, the mean and standard deviation of the array were computed. These values served as $\mu$ and $\sigma$ to normalize the T2-images of this specific patient. The equivalent was applied to the patient's DWI and ADC images, and the same process was employed for all patients separately.
Then, the dataset was augmented in the same way as the authors. Concretely, images were rotated ($-20$ to $20^\circ$), flipped horizontally (probability of $0.5$) and shifted horizontally (value $\in [-1, 0, 1]$ pixel). These techniques alone allowed to create a large enough amount of data. Therefore, two other augmentation methods used by the authors (horizontal stretching by a \mbox{factor $\in [0.9,1.1]$} and vertical shifting) were not used.

### 2020-03-25 Common/chapters/transfer_learning.tex
Julien and Johan: typos

\subsubsection{Manual transfer learning}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}The second Python script allows to perform each transfer learning step by hand. Thanks to this, a good combination of hyperparameters can be searched for without having to run the whole pipeline. The command line arguments slighty differ from the automated version. Table \ref{table:manual_transfer_learning_options} lists them. First of all, a single training set and a single validation set have to be specificied. In addition to this, a second dataset is required: the reference/target one, which does not change throughout the process. This dataset is useful for the global performance graphs (see Section \ref{sec:global_performance}). Another parameter used for the global performance graphs is the "-{}-last{\_}layer". Its role is limited to this, unless "-{}-{}attach{\_}DM" is set to "True". In this case, the decision maker loaded as "-{}-last{\_}layer" is attached to the current model, provided the current step is a frozen one. This option is used at the last frozen step (target dataset), as this decision maker comes from the first training (target dataset as well). Doing this instead of a using a new random decision maker (as it is the case for the non-target datasets) allows to start with a skilled decision maker and optimize it according to the features learned during the transfer learning. Furthermore, arguments which were comma-separated values become single values, as this file runs a single transfer learning step instead of seven. Also, an output name for Tensorboard needs to be specified. In the automated version, this output name is automatically handled by the code itself. The latter allows to organize the various graphs generated by Tensorboard within the Tensorboard interface. If it is used in a correct way, Tensorboard can then be run on the root directory containing all graphs (which may be in subdirectories).

>>>>

\subsubsection{Manual transfer learning}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Cl{\'e}ment}}The second Python script allows to perform each transfer learning step by hand. Thanks to this, a good combination of hyperparameters can be searched for without having to run the whole pipeline. The command line arguments slighty differ from the automated version. Table \ref{table:manual_transfer_learning_options} lists them. First of all, a single training set and a single validation set have to be specificied. In addition to this, a second dataset is required: the reference/target one, which does not change throughout the process. This dataset is useful for the global performance graphs (see Section \ref{sec:global_performance}). Another parameter used for the global performance graphs is the "-{}-last{\_}layer". Its role is limited to this, unless "-{}-{}attach{\_}DM" is set to "True". In this case, the decision maker loaded as "-{}-last{\_}layer" is attached to the current model, provided the current step is a frozen one. This option is used at the last frozen step (target dataset), as this decision maker comes from the first training (target dataset as well). Doing this instead of using a new random decision maker (as it is the case for the non-target datasets) allows to start with a skilled decision maker and optimize it according to the features learned during the transfer learning. Furthermore, arguments which were comma-separated values become single values, as this file runs a single transfer learning step instead of seven. Also, an output name for Tensorboard needs to be specified. In the automated version, this output name is automatically handled by the code itself. The latter allows to organize the various graphs generated by Tensorboard within the Tensorboard interface. If it is used in a correct way, Tensorboard can then be run on the root directory containing all graphs (which may be in subdirectories).
